Paper_analyses

### 2022-12-03 PCA figures1.Rmd
test for Review
recover the power analyses files

newDFscale_stim<- newDF$subject%>%
  group_by(subject, subject_orig)%>%
  mutate_if(is.numeric, scale)%>%
  group_by(stimuli, norm)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

@@

colnames(newDFscale_sid_norm)
res.MFA_stim_val_scal2e_sidnorm <-MFA(newDFscale_sid_norm[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

@@

res.MFA_stim_val_scal2e_stim <-MFA(newDFscale_stim[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

@@

  mfa_plots$groups  +p$graphstyle_int
```
```{r}
  mfa_plots$groups<-   mfa_plots$groups+
    # coord_fixed(ratio = 1)+
    p$graphstyle_int+
    theme(legend.title = element_blank())
  # 
  # 
  mfa_plots$groups<- mfa_plots$groups+    
    # p$graphstyle_int+
   guides(
  fill = guide_legend(

@@

>>>>

newDFscale_stim<- newDF%>%
  group_by(subject, subject_orig)%>%
  mutate_if(is.numeric, scale)%>%
  group_by(stimuli, norm)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

@@

colnames(newDFscale_sid_norm)
res.MFA_stim_val_scal2e_sidnorm <-MFA(newDFscale_sid_norm[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("categorical","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

@@

res.MFA_stim_val_scal2e_stim <-MFA(newDFscale_stim[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("categorical","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

res.MFA_stim_val_scal2e_sid <-MFA(newDFscale_sid[,1:6],group=c(1,3,2), type=c("n","c","c"),name.group=c("categorical","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

newDFscale_sid

@@

  mfa_plots$groups  +p$graphstyle_int
```

```{r}
  mfa_plots$groups<-   mfa_plots$groups+
    # coord_fixed(ratio = 1)+
    p$graphstyle_int+
    theme(legend.title = element_blank())
  # 
  # 
  mfa_plots$groups<- mfa_plots$groups+    
    # p$graphstyle_int+
   guides(
  fill = guide_legend(

@@

Supplementary materials

```{r}
plot.MFA(res.MFA_stim_val_scal2e_sidnorm)

SM_plots<- list()

SM_plots$sid_by_stimclass <-
plot.MFA(res.MFA_stim_val_scal2e_sidnorm, 
         choix="ind",
         partial='all',
         label = "norm",
         lab.par=TRUE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Factor map  \n aggregated by participant * stimulus category",
         alpha = .2,
         shadowtext = TRUE,
         cex = 1)+
  # # xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  # ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
  theme_classic()+
  p$graphstyle_int+
   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))

SM_plots$stim <- plot.MFA(res.MFA_stim_val_scal2e_stim, 
         choix="ind",
         partial='all',
         label = "norm",
         lab.par=TRUE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Factor map \n aggerated by stimulus id",
         alpha = .2,
         shadowtext = TRUE,
         cex = 1)+
  # # xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  # ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  # annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
  theme_classic()+
  p$graphstyle_int+
   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))

SM_plots$sid<- plot.MFA(res.MFA_stim_val_scal2e_sid, 
         choix="ind",
         partial='all',
         label = "norm",
         lab.par=TRUE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Factor map \n aggregated by participant id",
         alpha = .2,
         shadowtext = TRUE,
         cex = 1)+
  # # xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  # ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  # annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
  theme_classic()+
  p$graphstyle_int+
   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))

# Group representation
# sid_by_stimclass
SM_plots$sid_by_stimclas_GR<-  bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord),
          as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord.sup))%>%
  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord),
          as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord.sup))))%>%
  mutate(group = factor(group, levels = c("autonomic", "subjective","categorical"  ),
                        labels = c("autonomic","subjective","categorical")))%>%
  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
  geom_vline(xintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[1,1], linetype = "dashed")+
  geom_vline(xintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[2,1], linetype = "dashed")+
    geom_hline(yintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[1,2], linetype = "dashed")+
  geom_hline(yintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[2,2], linetype = "dashed")+
  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+

SM_plots$sid_by_stimclas_GR<- SM_plots$sid_by_stimclas_GR+
  p$graphstyle+
    scale_colour_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
    scale_fill_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
   theme(legend.position = "none",

# GR forSM_plots$stim <- plot.MFA(res.MFA_stim_val_scal2e_stim,

SM_plots$stim_GR<-  bind_rows(as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord),
          as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord.sup))%>%
  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord),
          as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord.sup))))%>%
  mutate(group = factor(group, levels = c("autonomic", "subjective","categorical"  ),
                        labels = c("autonomic","subjective","categorical")))%>%
  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
  geom_vline(xintercept = res.MFA_stim_val_scal2e_stim$group$coord[1,1], linetype = "dashed")+
  geom_vline(xintercept = res.MFA_stim_val_scal2e_stim$group$coord[2,1], linetype = "dashed")+
    geom_hline(yintercept = res.MFA_stim_val_scal2e_stim$group$coord[1,2], linetype = "dashed")+
  geom_hline(yintercept = res.MFA_stim_val_scal2e_stim$group$coord[2,2], linetype = "dashed")+
  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+

   # size = tyextsize*8
  geom_text(aes(x = Dim.1, y = Dim.2+.05, label = group, color = group 
               ), size = 8)+
    # annotate("text",label = group x = Dim.1, y = Dim.2))+
  xlim(0,1)+
  ylim(0,1)+
      theme_classic()+
      xlab("Dimension 1")+
   ylab("Dimension 2")+
  ggtitle("Groups representation")+
  scale_color_brewer(palette = "Dark2", direction = -1)+
    scale_fill_brewer(palette = "Dark2",direction = -1)+
  theme(legend.position = "none",

SM_plots$stim_GR <- SM_plots$stim_GR +
  p$graphstyle+
    scale_colour_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
    scale_fill_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
   theme(legend.position = "none",

SM_plots$stim_GR

# ssid
# SM_plots$sid<- plot.MFA(res.MFA_stim_val_scal2e_sid,

SM_plots$ssid_GR<-  bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord),
          as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord.sup))%>%
  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord),
          as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord.sup))))%>%
  mutate(group = factor(group, levels = c("autonomic", "subjective","categorical"  ),
                        labels = c("autonomic","subjective","categorical")))%>%
  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
  geom_vline(xintercept = res.MFA_stim_val_scal2e_sid$group$coord[1,1], linetype = "dashed")+
  geom_vline(xintercept = res.MFA_stim_val_scal2e_sid$group$coord[2,1], linetype = "dashed")+
    geom_hline(yintercept = res.MFA_stim_val_scal2e_sid$group$coord[1,2], linetype = "dashed")+
  geom_hline(yintercept = res.MFA_stim_val_scal2e_sid$group$coord[2,2], linetype = "dashed")+
  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+

   # size = tyextsize*8
  geom_text(aes(x = Dim.1, y = Dim.2-.1, label = group, color = group 
               ), size = 8)+
    # annotate("text",label = group x = Dim.1, y = Dim.2))+
  xlim(0,1)+
  ylim(0,1)+
      theme_classic()+
      xlab("Dimension 1")+
   ylab("Dimension 2")+
  ggtitle("Groups representation")+
  scale_color_brewer(palette = "Dark2", direction = -1)+
    scale_fill_brewer(palette = "Dark2",direction = -1)+
  theme(legend.position = "none",

SM_plots$ssid_GR<- SM_plots$ssid_GR +
  p$graphstyle+
    scale_colour_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
    scale_fill_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
   theme(legend.position = "none",

SM_plots$stim_GR 
SM_plots$ssid_GR

# correlation circles

SM_plots$cor_circle_sid_stim_cat<- plot.MFA(res.MFA_stim_val_scal2e_sidnorm, choix="var",habillage='group',title="Correlation circle",
         cex = 2.7) +
    xlim(-1,1)+
  scale_color_brewer(palette = "Dark2", direction = -1)+
  theme_classic()+

 # ggsave("cor_circle.tiff",   mfa_plots$cor_circle, device = "tiff", width = 10, height = 6, dpi = 800)

# cor circle stim

SM_plots$cor_circle_stim<- plot.MFA(res.MFA_stim_val_scal2e_stim, choix="var",habillage='group',title="Correlation circle",
         cex = 2.7) +
    xlim(-1,1)+
  scale_color_brewer(palette = "Dark2", direction = -1)+
  theme_classic()+

SM_plots$cor_circle_stim

### 2022-12-03 Paper_Analyses_subj_obje_arousal1.Rmd
test for Review
recover the power analyses files

@@

@@

@@

@@

>>>>

View(eigen_first)
eigen_first1<- eigen_first %>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  # gather(dimension, value_dimenion, -group, -sim_no) %>%
  group_by(component)%>%
  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE), 
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))

@@

res.mfa_bio_vs_self2_scale$eig[2,3]
```

@@

mfa_boot_corfirst<- left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension"))

mfa_boot_corfirst$measure<- if_else(mfa_boot_corfirst$variable == "log_BI", "SCR",
        if_else(mfa_boot_corfirst$variable == "Bio_Me", "HR",
                if_else(mfa_boot_corfirst$variable == "pup_ba", "pupil",
                if_else(mfa_boot_corfirst$variable == "arousa", "arousal",
                if_else(mfa_boot_corfirst$variable == "valenc", "valence",NULL)
                ))))

mfa_boot_corfirst$variable
left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension"))

mfa_boot_corfirst%>%
  subset(dimension == "Dim.1")%>%
  ggplot(aes(value_dimenion.x, color = measure)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  # geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 , linetype = measure))+ #color = "gray30"
  # facet_grid(~dimension)+
  geom_point(aes(x = value_dimenion.y, y = -2))+
    geom_vline(xintercept = 0,linetype = "dashed", alpha = .5, size = 1)+
  # facet_grid(~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  scale_color_brewer(palette = "Dark2")+

  theme_classic()+
  p$graphstyle_int

@@

library(boot)
library(rms)

??bootBCa

@@

left_join(groups_first_1boot_CIcorrected2, groups_first_obs,by = c("group", "dimension"))%>%
  subset(!is.na(value_dimenion))%>%
  group_by(dimension,group)%>%
   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[1],
         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[2])%>%
   ggplot(aes(value_dimenion, color = group)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +

  facet_grid(~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()
